\documentclass[11pt]{article}
\usepackage{fullpage}

\title{Customer Questionnaire}
\author{Rane Brown and Brian Douglass}
\date{\today}

\begin{document}
	\maketitle

	\section*{Product Overview}
		Our product idea is to create a motor system that is capable of automatically raising and lowering a set of blinds. The motor batteries will be charged using a small solar panel that attaches to the window. This will eliminate the need to change the batteries on the system. We will also create a mobile phone app that is capable of controlling the blinds via bluetooth. This app will enable the user to set a schedule for when the blinds open and close or set them to open and close based on the amount of light outside. If time permits, we would also add wireless connectivity to our product so the blinds could be controlled when the user is away from the house. There are already products on the market that offer similar functionality but the price for these product is \$100 or more. In addition, these products often require professional installation. Our product will cost less than \$20 and take less than 10 minutes to install. 

	\section*{Question 1}
		Would you be interested in the described product? Why?
		\vspace{.8 in}

	\section*{Question 2} 
		What features of automatic opening blinds are most important to you?
		\newpage

	\section*{Question 3}
		Do you manually raise and lower blinds in your home frequently? How frequently?
		\vspace{.8 in}

	\section*{Question 4}
		Have you considered purchasing automatic blinds before? Why or why not?
		\vspace{.8 in}

	\section*{Question 5}
		Why is home connectivity important to you? (Controlling items in home through wireless means.)
		\vspace{.8 in}

	\section*{Question 6}
		Do you have any suggestions for improvements?
		\vspace{.8 in}

	\section*{Additional Comments}
		\vspace{.8 in}

\end{document}